Log or not - Analysis of ECDC forecasts

### 2022-01-28 analysis/Analysis ECDC forecasts.Rmd
update plots

```{r}
# load data 
# ------------------------------------------------------------------------------

hub_data <- rbindlist(list(
  fread(here("data", "full-data-european-forecast-hub-1.csv")), 
  fread(here("data", "full-data-european-forecast-hub-2.csv"))
)) |>
  unique()
```

@@

>>>>

```{r}
# load data 
# ------------------------------------------------------------------------------
hub_data <- rbindlist(list(
  fread(here("data", "full-data-european-forecast-hub-1.csv")), 
  fread(here("data", "full-data-european-forecast-hub-2.csv")),
  fread(here("data", "full-data-european-forecast-hub-3.csv"))
)) |>
  unique()
```

@@

wis_vs_total <- function(scores, summary_fct = mean, fulldata = hub_data) {

  total_values <- 
    fulldata |> 
    filter(!is.na(prediction)) |>
    group_by(location, target_type, target_end_date) |>
    summarise(true_value = unique(true_value)) |>
    group_by(location, target_type) |>
    summarise(total = sum(true_value))

  scores |> 
  filter(model == "EuroCOVIDhub-ensemble", 
         horizon == 2) |>
  group_by(target_type, location, scale) |>
  summarise(wis = summary_fct(interval_score), 
            .groups = "drop_last") |> 
  inner_join(total_values) |>
  ggplot(aes(y = wis, x = total)) + 
  geom_point() + 
  facet_wrap(~ target_type + scale, scale = "free") + 
  theme_minimal() + 
  theme(legend.position = "none") + 
  # scale_x_continuous(labels = scale_fn) + 
  # scale_y_continuous(labels = scale_fn) + 
  scale_x_continuous(labels = scale_fn, trans = "log10") +
  scale_y_continuous(labels = scale_fn, trans = "log10") +
  labs(y = "REPLACE", x = "Total number of observed values")
}

mean_wis_vs_total <- wis_vs_total(scores)
ggsave("output/figures/HUB-mean-scores-vs-total.png", width = 7, height = 5)

sd_wis_vs_total <- wis_vs_total(scores, summary_fct = stats::sd)
ggsave("output/figures/HUB-sd-scores-vs-total.png", width = 7, height = 5)
